Visualizing Independence Using Extended Association and Mosaic Plots

### 2006-05-26 trunk/vcd/paper/DSC-2003/draft.Rnw
re-organized papers, added color draft
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@536 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\title{Visualizing Independence Using Extended Association and Mosaic Plots}
\author{\hfill Achim Zeileis$^\dag$ \hfill David Meyer$^\dag$ \hfill Kurt Hornik$^\ddag$ \hfill \hfill \\[0.2cm]
\dag {\it \small Institut f\"ur Statistik \& Wahrscheinlichkeitstheorie,
 Technische Universit\"at Wien}\\
\ddag {\it \small Institut f\"ur Statistik, Wirtschaftsuniversit\"at Wien}
}
\date{}
\maketitle

>>>>

\title{Visualizing Independence Using Extended Association and Mosaic Plots}
\author{\hfill Achim Zeileis$^\dag$ \hfill David Meyer$^\ddag$ \hfill Kurt Hornik$^\dag$ \hfill \hfill \\[0.2cm]
\dag {\it \small Institut f\"ur Statistik \& Mathematik, Wirtschaftsuniversit\"at Wien}\\
\ddag {\it \small Institut f\"ur , Wirtschaftsuniversit\"at Wien}
}
\date{}
\maketitle
